Benefits and risks of diversification for individual fishers

### 2017-02-10 portfolio/text/anderson-etal-rev-pfx.tex
Edits

% Please add here a significance statement to explain the relevance of your work
% <120 words
\significancestatement{
Individuals relying on natural resources to sustain their livelihoods,
such as fishers, farmers, and forestry workers,
face high levels of income variability.
For fishers, targeting a diversity of species has been shown to
reduce community- and vessel-level revenue variability
but the individual-level consequences are unknown.
Our work demonstrates that individuals in fisheries targeting
a diversity of species
and individuals that participate in multiple fisheries
buffer income variability compared to less diverse individuals.
However, adjusting (increasing or decreasing) species diversity from year-to-year
usually increases individual-level revenue variability.
\textbf{OR}
However, specializing from year-to-year
(reducing species diversity)
tends to be associated with increased revenue
as well as increased revenue variability
when controlling for effort.
The most effective option for individuals to
reduce revenue variability via diversification
--- purchasing additional permits ---
is also expensive, often limited by regulations,
and therefore unavailable to many.
}
% We ask how multiple forms of
% species diversification affect individual-level
% revenue and revenue variability for Alaskan fishers.

>>>>

% Please add here a significance statement to explain the relevance of your work
% <120 words
\significancestatement{
Individuals relying on natural resources to sustain their livelihoods,
such as fishers, farmers, and forestry workers,
face high levels of income variability.
For fishers in particular, targeting multiple species has been shown to
reduce revenue variability at large scales (vessels and communities)
but the individual-level consequences are unknown.
Our work demonstrates that individuals in fisheries targeting
a diversity of species
and individuals that participate in multiple fisheries
buffer income variability compared to less diverse individuals.
However, large adjustments in diversification strategies from year-to-year appear risky and
usually increase revenue variability.
% \textbf{OR}
% However, specializing from year-to-year
% (reducing species diversity)
% tends to be associated with increased revenue
% as well as increased revenue variability
% when controlling for effort.
The most effective option for individuals to
reduce revenue variability via diversification
--- purchasing additional permits ---
is also expensive, often limited by regulations,
and therefore unavailable to many.
}
% We ask how multiple forms of
% species diversification affect individual-level
% revenue and revenue variability for Alaskan fishers.
